\emph{MixFishSim}: highly resolved spatiotemporal simulations for exploring mixed fishery dynamics

### 2019-04-14 write_up/mixfishsim_ecolmod.tex
Discussion update

Our study evaluates the importance of data scaling and considers potential
biases introduced through data aggregation when using commercial fisheries
logbooks and Vessel Monitoring Systems for inference on spatio-temporal
dynamics in fisheries. Understanding how fishers exploit multiple
heterogeneously distributed fish populations with different catch limits or
conservation status requires detailed understanding of the overlap of
resources; this is difficult to achieve using conventional modelling approaches
due to the patchy and irregular nature of fisheries resulting in preferential
sampling \cite{Martinez-Minaya2018}. Often data is aggregated or extrapolated
which requires assumptions about the spatial and temporal scale of processes.
Our study explores the assumptions behind such aggregation and preferential
sampling to identify potential impacts on management advice. With modern
management approaches increasingly employing more nuanced spatio-temporal
approaches in order to maximise productivity while taking account of both the
biological and human processes operating on different time-frames
\cite{Dunn2016}, understanding assumptions behind the data used is vital to
ensure measures are effective. \\

>>>>

Our study evaluates the importance of data scaling and considers potential
biases introduced through data aggregation when using commercial fisheries data
for inference on spatio-temporal dynamics in fisheries. Understanding how
fishers exploit multiple heterogeneously distributed fish populations with
different catch limits or conservation status requires detailed understanding
of the overlap of resources; this is difficult to achieve using conventional
modelling approaches due to the patchy and irregular nature of fisheries
resulting in preferential sampling \cite{Martinez-Minaya2018}. Often data is
aggregated or extrapolated which requires assumptions about the spatial and
temporal scale of processes. Our study explores the assumptions behind such
aggregation and preferential sampling to identify potential impacts on
management advice. With modern management approaches increasingly employing
more nuanced spatio-temporal approaches in order to maximise productivity while
taking account of both the biological and human processes operating on
different time-frames \cite{Dunn2016}, understanding assumptions behind the
data used - increasingly a combination of logbook and positional information
from vessel monitoring systems - is vital to ensure measures are effective. \\
